### 2013-11-13 research/MCR report/main.tex
uploaded 13-11-2013 7.05 pm

\documentclass{article}  
\usepackage{a4wide}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{tabulary}
%\usepackage[sort]{cite}
%\usepackage[sort,nocompress]{cite}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{placeins}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{epstopdf}
\usepackage{enumerate}
\usepackage{pdfpages}
\newcommand{\hilight}[1]{\colorbox{yellow}{#1}}

@@

%\year{April, 2004} 
%\department{\emph{Department of Electrical and Computer Systems Engineering}}
%\title{Towards a Green Optical Internet}
%\author{Nishan Dharmaweera \and Rajendran Parthiban \and Y. Ahmet \c{S}ekercio\u{g}lu}
\begin{document}

@@

In order to carry out an optimisation study on the fluid dynamics portion of the system, it is essential to study underlying fluid mechanics for galloping. It has been already established by \cite{Parkinson1964} that the instantaneous lift is the input of the system. Therefore it is essential to have an understanding on how exactly this lift occur. According to \cite{Parkinson1989},\hilight{Luo 94} the lift force is created by the secondary flow of the two shear layers of either side of the body which creates an unbalanced pressure distribution on the afterbody. If a square cross section is taken as an example, when the body have a transverse $\dot{y}$, the relative velocity causes an instantaneous angle of attack which makes one shear layer lies closer to the body than the other. Therefore the shear layer near the body creates a pressure imbalance by creating a higher suction on the wall of the body on the adjacent side than the suction caused by the shear layer on the opposite side on its adjacent side of the body. The lift force become its maximum when the shear layer closer to the body re attaches at the trailing edge. As the angle of attack is further increased, the separated shear layer in the opposite side of the body (which was initially away from the body) shrinks therefore the pressure difference decreases which results a decrease in the lift force. This explanation was validated by \cite{Luo1994} by conducting flow visualisation experimentally.

@@

%\section{Difficulties and challenges} 
%%
%%\begin{enumerate}
%%      
%%\end{enumerate}
\bibliographystyle{elsarticle-harv}
\bibliography{../bibtex/paper}
%\appendix
%%\begin{center}
%%\section*{\LARGE Appendix 1}
%%\addcontentsline{toc}{section}{Appendix 1} 
%%\end{center}
Proposed table of contents of the final PhD thesis:
\begin{enumerate}
\item Preliminary remarks 
\item A review of literature
\begin{enumerate}[i]
\item Introduction
\item Flow induced vibrations 
\item Flow induced vibrations as a mechanism of energy harvesting
\item Aeroelastic galloping
\item Behaviour of shear layer 
\end{enumerate}
\item Methodology and validation
\begin{enumerate}[i]
\item Introduction
\item Governing equations and quasi-steady state model 
\item Numerical methods and boundary conditions 
\item The governing equations for the DNS method: Naiver-Stokes and continuity  
\item Discretisation  
\item Integration of substep equation 
\item Boundary conditions 
\item Spectral element method
\item Convergence and validation studies 
\item Summary
\end{enumerate}
\item Power analysis for high and low Reynolds numbers
\begin{enumerate}[i]
\item Introduction 
\item Stationary data 
\item Natural frequency 
\item Damping constant 
\item Mass ratio
\item FSI validation 
\item Summary 
\end{enumerate}

>>>>

\documentclass{article}  
\usepackage{a4wide}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
%\usepackage{url}
\usepackage{tabulary}
%\usepackage[sort]{cite}
%\usepackage[sort,nocompress]{cite}
\usepackage{multirow}
\usepackage{booktabs}
%\usepackage{placeins}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{epstopdf}
\usepackage{enumerate}
\usepackage{pdfpages}
\newcommand{\hilight}[1]{\colorbox{yellow}{#1}}

@@

%\year{April, 2004} 
%\department{\emph{Department of Electrical and Computer Systems Engineering}}
%\title{Towards a Green Optical Internet}
%\author{Nishan Dharmaweera \and Rajendran Parthiban \and Y. Ahmet \c{S}ekercio\u{g}lu}

\begin{document}

@@

In order to carry out an optimisation study on the fluid dynamics portion of the system, it is essential to study underlying fluid mechanics for galloping. It has been already established by \cite{Parkinson1964} that the instantaneous lift is the input of the system. Therefore it is essential to have an understanding on how exactly this lift occur. According to \cite{Parkinson1989},\hilight{Luo 94} the lift force is created by the secondary flow of the two shear layers of either side of the body which creates an unbalanced pressure distribution on the afterbody. If a square cross section is taken as an example, when the body have a transverse $\dot{y}$, the relative velocity causes an instantaneous angle of attack which makes one shear layer lies closer to the body than the other. Therefore the shear layer near the body creates a pressure imbalance by creating a higher suction on the wall of the body on the adjacent side than the suction caused by the shear layer on the opposite side on its adjacent side of the body. The lift force become its maximum when the shear layer closer to the body reattaches at the trailing edge. As the angle of attack is further increased, the separated shear layer in the opposite side of the body (which was initially away from the body) shrinks therefore the pressure difference decreases which results a decrease in the lift force. This explanation was validated by \cite{Luo1994} by conducting flow visualisation experimentally.

@@

%\section{Difficulties and challenges} 
%%
%%\begin{enumerate}
%%      
%%\end{enumerate}
\bibliographystyle{elsarticle-harv}

\bibliography{../bibtex/paper}
\appendix
\begin{center}
\section*{\LARGE Appendix 1}
\addcontentsline{toc}{section}{Appendix 1} 
\end{center}
Proposed table of contents of the final PhD thesis:
\begin{enumerate}
\item Preliminary remarks 
\item A review of literature
\begin{enumerate}[i]
\item Introduction
\item Flow induced vibrations 
\item Flow induced vibrations as a mechanism of energy harvesting
\item Aeroelastic galloping
\item Behaviour of shear layer 
\end{enumerate}
\item Methodology and validation
\begin{enumerate}[i]
\item Introduction
\item Governing equations and quasi-steady state model 
\item Numerical methods and boundary conditions 
\item The governing equations for the DNS method: Naiver-Stokes and continuity  
\item Discretisation  
\item Integration of substep equation 
\item Boundary conditions 
\item Spectral element method
\item Convergence and validation studies 
\item Summary
\end{enumerate}
\item Power analysis for high and low Reynolds numbers
\begin{enumerate}[i]
\item Introduction 
\item Stationary data 
\item Natural frequency 
\item Damping constant 
\item Mass ratio
\item FSI validation 
\item Summary 
\end{enumerate}

### 2013-11-13 research/paper/results/results-2.3.tex
uploaded 13-11-2013 7.05 pm

In this paper, the power transfer of a square body under aero elastic galloping is analysed by solving the quasi-steady state model equations through numerical integration. The power output of the system is not dependent on \ustar or natural frequency of the system, but dependent on the transverse velocity amplitude of the system. This is shown by the collapsed plots in terms of non-dimensionalised damping constant (using flow parameters). By analysing key regions of the power vs \ustar curve it could be concluded that in order to obtain an optimum power output, the damping constant ($\frac{c}{\rho\mathcal{A}U}$) should be high, but not excessive until it  to hinders the galloping from reaching induced angles of attack where the forcing is significant. The effect of mass ratio was could also be observed where at \reynoldsnumber=165 the mean power tend to decrease at $m^*<40$ which was found out to be an influence of vortex shedding. At \reynoldsnumber=22300 an opposite result could be observed where the mean power tend to increase with decreasing mass ratio as well as the mean power tend to increase with increasing $U^*$ at low mass ratios. The cause for this was found out to be the fact that as the mass ratio decreases, due to the lower inertia the velocity sinusoidal signal tend to move towards a square signal where it sustains high velocities for longer periods of time which leads to a higher mean power output.

>>>>

In this paper, the power transfer of a square body under aero elastic galloping is analysed by solving the quasi-steady state model equations through numerical integration. The power output of the system is not dependent on \ustar or natural frequency of the system, but dependent on the transverse velocity amplitude of the system. This is shown by the collapsed plots in terms of non-dimensionalised damping constant (using flow parameters). By analysing key regions of the power vs \ustar curve it could be concluded that in order to obtain an optimum power output, the damping constant ($\frac{c}{\rho\mathcal{A}U}$) should be high, but not excessive until it  to hinders the galloping from reaching induced angles of attack where the forcing is significant. The effect of mass ratio was could also be observed where at \reynoldsnumber=165. The mean power tend to decrease at $m^*<50$ which was found out to be an influence of vortex shedding. At \reynoldsnumber=22300 an opposite result could be observed where the mean power tend to increase with decreasing mass ratio as well as the mean power tend to increase with increasing $U^*$ at low mass ratios. The cause for this was found out to be the fact that when the mass ratio decreases, due to the lower inertia the velocity time trace tend to move from a sinusoidal signal towards a square signal where it sustains high velocities for longer periods of time which leads to a higher mean power output.
